Untitled

### 2024-01-04 code/analysis_Redo.Rmd
testing other quality effects

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  #mutate(Qcomp = (htn.rate + dm.rate) / 2) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total, Qcomp, Altman, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)

>>>>

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  #mutate(Qcomp = (crc.rate + pap.rate + adultbmi.rate + childbmi.rate) / 4) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total, Qcomp, Altman, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)
